---
title: "HW5"
author: "Sarahy Martinez"
date: "2024-11-05"
output: github_document
---

```{r}
library(tidyverse)
library(rvest)
library(stringr)
library(tibble)
library(patchwork)
```


# Problem 1 

```{r}

same_birthday = function(n) { 
  birthday = sample(1:365, n, replace = TRUE)
  return(length(birthday) != length(unique(birthday))) 
  }

n = 30 
results = same_birthday(n) 

# False -> all birthdays are unique , TRUE -> there are duplicate birthdays 

```

```{r}

simulate_probabilities = function(group_size, num_simulations) {
  results = map(1:num_simulations, ~same_birthday(group_size))
  mean(unlist(results)) }

group_sizes = 2:50 
probabilities = map_dbl(group_sizes, ~simulate_probabilities(.x, 10000))


results_table = tibble(
  group_size = group_sizes, probability = probabilities)

```

```{r}

ggplot( results_table, aes( x = group_size, y = probability)) + geom_line() + geom_point()+
  labs (
    title = "Group Size vs Probaility of Same Birthday ",
    x = "Group Size",
    y = "Probability"
  )

```


# Problem 2

## Problem 2a
```{r}

sim_power= function(mu, n = 30, sigma = 5, datasets = 5000, alpha = 0.05) {
  results = replicate(datasets, {
    x = rnorm(n, mean = mu, sd = sigma)
    test = t.test(x, mu = 0)
    broom::tidy(test)
  }, simplify = FALSE)
  
  results_df = bind_rows(results)
  
  power = mean(results_df$p.value < alpha)
  
  avg_mu_hat = mean(results_df$estimate) 
  avg_mu_hat_rejected = mean(results_df$estimate[results_df$p.value < alpha])
  
return(list(mu_hat = avg_mu_hat, power = power, avg_mu_hat_rejected = avg_mu_hat_rejected))
  }


mu_values =0:6

results = vector("list", length(mu_values))

for( i in 1:length(mu_values)){
  mu = mu_values[i]
  results[[i]] = sim_power(mu)

}

results_df = bind_rows(results) %>% 
  mutate(mu = mu_values)


```


## Problem 2B
```{r}

ggplot( results_df, aes( x = mu, y = power)) + geom_line() + geom_point()+
  labs (
    title = " Proportion of Times Null Was Rejected vs Mu",
    x = "True Value of Mu",
    y = "Power"
  )

```
Based  on the graph we can see that as effect size increases so does power. There is a positive association until we reach mu=5 and mu =6 where power starts to plateau and even out. 

## Problem 2C

```{r}
mu_true = ggplot( results_df, aes( x = mu, y = mu_hat)) + geom_line() + geom_point()+
  labs (
    title = " Average Estimate of Mu hat vs True Value Mu",
    x = "True Value of Mu",
    y = "Avg estimate of Mu hat"
  )

```


```{r}

mu_mu_rejected = ggplot( results_df, aes( x = mu, y = avg_mu_hat_rejected)) + geom_line() + geom_point()+
  labs (
    title = " Average Estimate of Mu hat Rejected vs True Value Mu",
    x = "True Value of Mu",
    y = "Avg estimate of Mu hat rejected"
  )


```

Overlaying the graphs

```{r}
(mu_true/ mu_mu_rejected)

```
The plot of the average estimate of mu hat vs mu demonstrates a positive linear relationship, as true value of mu increases so does the average estimate of mu hat. For the second plot of the Average Estimate of Mu hat rejected vs the true mu we can see that there is also a positive association however their trends differ. For instance, from 0-1 the true value of mu increases linearly but after that it begins to increase exponentially at 2 and on wards. Lastly, we can conclude that the sample average of mu hat across the tests for which the null is rejected approximately equal to the true value of mu because of their linear relationship; they both share the almost the same unit increase/ slope. 















