---
title: "HW5"
author: "Sarahy Martinez"
date: "2024-11-05"
output: github_document
---

```{r}
library(tidyverse)
library(rvest)
library(stringr)
library(tibble)
library(patchwork)
```


# Problem 1 

```{r}

same_birthday = function(n) { 
  birthday = sample(1:365, n, replace = TRUE)
  return(length(birthday) != length(unique(birthday))) 
  }

n = 30 
results = same_birthday(n) 

# False -> all birthdays are unique , TRUE -> there are duplicate birthdays 

```

```{r}

simulate_probabilities = function(group_size, num_simulations) {
  results = map(1:num_simulations, ~same_birthday(group_size))
  mean(unlist(results)) }

group_sizes = 2:50 
probabilities = map_dbl(group_sizes, ~simulate_probabilities(.x, 10000))


results_table = tibble(
  group_size = group_sizes, probability = probabilities)

```

```{r}

ggplot( results_table, aes( x = group_size, y = probability)) + geom_line() + geom_point()+
  labs (
    title = "Group Size vs Probaility of Same Birthday ",
    x = "Group Size",
    y = "Probability"
  )

```


# Problem 2

## Problem 2a
```{r}

sim_power= function(mu, n = 30, sigma = 5, datasets = 5000, alpha = 0.05) {  #defining the results
  results = replicate(datasets, { # use replicate to simulate the sampling of 5000 times
    x = rnorm(n, mean = mu, sd = sigma) # defining the variables 
    test = t.test(x, mu = 0)  # set mu to 0 
    broom::tidy(test)   # tidy the results 
  }, simplify = FALSE) 
  
  results_df = bind_rows(results)  # binding the results of the df
  
  power = mean(results_df$p.value < alpha)  # calculating power of the p-value 
  
  avg_mu_hat = mean(results_df$estimate)  # want the avg mu so take the mean across the estimates
  avg_mu_hat_rejected = mean(results_df$estimate[results_df$p.value < alpha])  # want the p value rejected of less than 0.05 and take the mean of that 
  
return(list(mu_hat = avg_mu_hat, power = power, avg_mu_hat_rejected = avg_mu_hat_rejected))  #mapping results above results to this 
  }


mu_values =0:6   #defining the values mu = 1,2,3,4,5,6 ; couldn't do (1,2,3,4,5,6) so did 0:6

results = vector("list", length(mu_values))   # mapping the list 

for( i in 1:length(mu_values)){   # for loop of the length for each iteration length  of the mu value 
  mu = mu_values[i]
  results[[i]] = sim_power(mu)

}

results_df = bind_rows(results) %>%   # binding the rows to have a tibble and then mutating mu to mu values 
  mutate(mu = mu_values)


```


## Problem 2B
```{r}

ggplot( results_df, aes( x = mu, y = power)) + geom_line() + geom_point()+
  labs (
    title = " Proportion of Times Null Was Rejected vs Mu",
    x = "True Value of Mu",
    y = "Power"
  )

```
Based  on the graph we can see that as effect size increases so does power. There is a positive association until we reach mu=5 and mu =6 where power starts to plateau and even out. 

## Problem 2C

```{r}
mu_true = ggplot( results_df, aes( x = mu, y = mu_hat)) + geom_line() + geom_point()+
  labs (
    title = " Average Estimate of Mu hat vs True Value Mu",
    x = "True Value of Mu",
    y = "Avg estimate of Mu hat"
  )

```


```{r}

mu_mu_rejected = ggplot( results_df, aes( x = mu, y = avg_mu_hat_rejected)) + geom_line() + geom_point()+
  labs (
    title = " Average Estimate of Mu hat Rejected vs True Value Mu",
    x = "True Value of Mu",
    y = "Avg estimate of Mu hat rejected"
  )


```

Overlaying the graphs

```{r}
(mu_true/ mu_mu_rejected) # pathwork to overlay?

```
The plot of the average estimate of mu hat vs mu demonstrates a positive linear relationship, as true value of mu increases so does the average estimate of mu hat. For the second plot of the Average Estimate of Mu hat rejected vs the true mu we can see that there is also a positive association however their trends differ. For instance, from 0-1 the true value of mu increases linearly but after that it begins to increase exponentially at 2 and on wards. Lastly, we conclude that the sample average of mu hat across the tests for which the null is rejected is approximately equal to the true value of mu because of there is somewhat of a linear relationship. If the linear relationship were to be full linear then the slopes would be the same and they would be equal to each other however in this graph it starts linear from 0-1 and then increases exponentially.

## Question 3 

```{r}




```












